\documentclass[main.tex]{subfiles}

\setcounter{secnumdepth}{2}

\begin{document}

\setcounter{section}{8}

\linksection{Лекция 13.03.2024 (Смольская Н.Б.)}

\sublinksection{Сослагательное наклонение}

%Определите, какой из подчёркнутых элементов предложения содержит ошибку.
%\vspace{2mm}

\begin{enumerate}[nosep,leftmargin=*]
	\item If the ozone gases of the atmosphere \textbf{hadn't filtered out} the ultraviolet rays of the sun, life, as we know it, would not have evolved on earth.
	\item I wish that me university \textbf{were} as large as state University because our facilities are more limited than theirs.
	\item Neither the mathematics department nor the biology department at the University requires that the student \textbf{should write} a thesis in order to graduate with a master's degree.
	\item When a patient's blood pressure is much higher than it should be, a doctor usually insists that he \textbf{should not smoke}.
	\item If you will \textbf{bought} one box at the regular price, you would receive another one at no extra cost.
	\item If Robert Kennedy \textbf{had lived} a little longer, he probably would have won the election.
	\item If it were \textbf{too} far from the Sun, the Earth would be too cold to support any living things.
	\item If the world was considered one big country its income inequality \textbf{would surpass} that of any actual country in the world today.
	\item Some executives insist that the secretary \textbf{should be} responsible for writing all reports as well as for balancing the books.
	\item The states require that every citizen \textbf{should register} before voting in an election.
\end{enumerate}

\end{document}
