\documentclass[main.tex]{subfiles}

\begin{document}

\linksection{Лекция 14.05.2024 (Смольская Н.Б.)}

\sublinksection{Лексико-грамматический тест}

\hypertarget{ltask:2024-05-14}{--- Выполнение заданий ---} (\hyperref[task:2024-05-14]{\color{blue}{перейти к тексту заданий}})
\\

\textbfind{Выполненное первое задание.}

\begin{enumerate}[nosep,leftmargin=10mm]
	\itemsep\eitsp
	\setcounter{enumi}{0}
	\item Agnostic -- (d) one who believes that God is unknowable
	\item Prognosis -- (f) a forecast or prediction
	\item Archetype -- (h) a perfect example of, as one of a group
	\item Paradoxical -- (i) self-contradictory, or apparently so
	\item Anachronism -- (a) the representation of smth. out of its right place in time
	\item Pathology -- (j) characteristics of a disease taken together
	\item Amorphous -- (c) without specific shape
	\item Apathy -- (b) the absence of caring about anything
	\item Sophisticated -- (e) wise in the ways of the world
	\item Prologue -- (g) introductory material
\end{enumerate}
\ 


\textbfind{Выполненное второе задание.}

Geographers \uline{(11) \textbf{legitimately}} complain that their discipline is \uline{(12) \textbf{misunderstood}} by the public for whom it remains the capitals of countries, the heights of mountains and \uline{(13) \textbf{lengths}} of rivers.
But Geography is not a static inventory of \uline{(14) \textbf{unrelated}} facts.
It \uline{(15) \textbf{analyzes}} why things are where they are. Even if we haven't \uline{(16) \textbf{personally}} experienced earthquakes, floods or famines, we are more \uline{(17) \textbf{aware}} today of the shifting face of the planet-rivers change their course, mountains rise, \uline{(18) \textbf{productive}} land may become infertile through poor techniques of \uline{(19) \textbf{cultivation}} and \uline{(20) \textbf{irrigation}} may make the desert bloom.
\\

\textbfind{Выполненное третье задание.}

\begin{enumerate}[nosep,leftmargin=10mm]
	\itemsep\eitsp
	\setcounter{enumi}{20}
	\item \uline{A}(A) strong painkiller is \uline{the most effective}(B) way of \uline{getting rid}(C) \uline{\textbf{of} (\sout{from})}(D) a headache.
	\item \uline{From}(A) primate research have come some of the \uline{\textbf{most} (\sout{mostly})}(B) important \uline{advances}(C) in modern \uline{medical}(D) history.
	\item This composition is \uline{\textbf{too} (\sout{enough})}(A) \uline{complicated}(B) \uline{for me}(C) \uline{to write}(D).
	\item There is no point in \uline{\textbf{trying} (\sout{to try})}(A) \uline{to convince}(B) him, he never listens \uline{to}(C) \uline{anybody}(D).
	\item Paper can be made \uline{from}(A) wood pulp \uline{by}(B) either a \uline{mechanical}(C) \uline{\textbf{or} (\sout{and})}(D) a chemical process.
\end{enumerate}
\ 

\textbfind{Выполненное четвёртое задание.}

\begin{enumerate}[nosep,leftmargin=10mm]
	\itemsep\eitsp
	\setcounter{enumi}{25}
	\item We \uline{\textbf{were allowed}} to leave early yesterday.
	\item The currency \uline{\textbf{has been devalued}} twice since the war.
	\item San Paulo \uline{\textbf{is said}} to be the fastest growing city in South America.
	\item Hard hats must \uline{\textbf{be worn}} while construction work is being carried out.
	\item The Opposition have asked for fuel taxes \uline{\textbf{to be reduced}}.
	\item This property \uline{\textbf{has been neglected}} totally since 1920 and is in need of major restoration.
	\item The report \uline{\textbf{will have been handed in}} by tomorrow morning.
	\item It's worth having the dishes \uline{\textbf{being washed}}.
	\item She \uline{\textbf{is thought}} to have left the country.
	\item To be able to qualify as an interpreter, many years of intensive language study \uline{\textbf{are required}}.
	\item Sometimes adolescents complain about not \uline{\textbf{being understood}} by their parents.
	\item The profit are supposed \uline{\textbf{to be divided}} among the shareholders.
	\item[39.] The winner of the race \uline{\textbf{hasn't been announced}} yet.
	\item[40.] A shortage of water is a problem in many parts of the world.
In some areas, water \uline{\textbf{is being taken}} from the ground faster than nature can replenish the supply.
	\item[42.] Pesticides should never \uline{\textbf{be used}} around water resources.
	\item[43.] Even though construction costs are high, a new dormitory \uline{\textbf{will be built}} next year.
	\item[44.] The benefits of exercise \uline{\textbf{are stressed}} by doctors, who know how important a healthy heart is.
	\item[45.] He was the first athlete \uline{\textbf{being disqualified}} for use of anabolic drugs.
	\item[46.] Men \uline{\textbf{are supposed}} to cover up such feelings as fear or grief.
	\item[47.] This programme \uline{\textbf{was recorded}} in front of a live audience yesterday.
	\item[48.] The matter \uline{\textbf{is being looked into}} at the moment.
	\item[49.] Most people believe that the light bulb \uline{\textbf{was invented}} by Thomas Edison.
	\item[50.] We regret to inform you that your request \uline{\textbf{has been denied}}.
\end{enumerate}
\ 



\end{document}
